### 2020-11-12 doc/manuscript/Dow_manuscript.Rmd
add mean growth parameters table

#Table numbers
hypothesis_table=1
species_table=2

@@

>>>>

#Table numbers
hypothesis_table=1
species_table=2
mean_growth_parameters_table=3

@@

```{r mean_growth_parameters_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
mean_growth_parameters <- read.csv("tables_figures/mean_growth_parameters.csv",stringsAsFactors = FALSE, check.names = FALSE)
knitr::kable(mean_growth_parameters) 
```
